Insert the article title here

### 2018-03-26 writeup/manuscript.tex
Minor edits to manuscript
Added in some missing details

\author{%%%% Author details
Alasdair D. F. Clarke$^1$, Jess Irons$^2$, Warren James$^2$, Andrew Leber$^2$ and Amelia R Hunt$^3$}

@@

\subsection{Participants}
We aim to find 64 participants to volunteer to take part in this experiment. Participants will be students from the University of Aberdeen. Some will be compensated with course credit and some will be paid \pounds 10 for their time. Sample size was determined in part due to constraints with counter-balancing; there are 16 different possible orders of tasks/conditions; we will run four participants in each order for a total of 64. All participants will sign a form giving informed consent. The study has already been approved by the University of Aberdeen Psychology Ethics Committee.

@@

Stimuli consisted of arrays of black oriented line segments against a grey background. The target was oriented $45^{\circ}$ clockwise, while the distracter items had a random orientiaton with a mean of $45^{\circ}$ anti-clockwise. The varience was low (xxx) on one half of the display to create a homogeneous texture, and high (xxx) on the other side to create a heterogeneous texture. This means that when the target is present on the homogeneous side of the stimulus, it can be easily be detected with peripheral vision, but when it is in the heterogeneous half, it is much harder to detect. There were a total of xxx trials and homo- and heterogeneous sides of the display were randomly vaired from trial to trial.

The position of the dominant eye was recorded using a desktop-mounted EyeLink 1000 eye
tracker (SR Research, Canada) sampling eye position at 1000 Hz.
This paradigm was carried out twice to give us an estiamte of how consistent participants are in their search strategy over time. The two sessions were indentical.

@@

In order to characterise an individual's behaviour in this task, we will compute the proportion of the first $n$ fixations that were on heterogeneous (difficult) side of the stimuli, over all target absent trials\footnote{Only take correct trials?}. \cite{nowakowsak2017} demonstrated a strong correlation between an this metric (for $n=5$) and reaction times ($r=$). However, a re-analysis of their data shows that an even stronger correlation is obtained with $n=3$.

@@

\subsection{Split-half Array Search}
Our results are broadly in line with \cite{nowakowsak2017}. The correlation between accuracy and reaction times between the two sessions is shown in Figure \ref{fig:splithalf_summary}(a, b). We can clearly see that there are large differences from one participant to the next in terms of both the proportion of hard targets found, and reading times. Furthermore, test-retest reliability appears to be reasonable, with correlations of around $r = 0.78$ (the value of $r = 0.71$ or easy targets is slightly lower, likely due to the restricted range).

>>>>

\author{%%%% Author details
Alasdair D. F. Clarke$^1$, Jess Irons$^2$, Warren James$^3$, Andrew Leber$^2$ and Amelia R Hunt$^3$}

@@

\subsection{Participants}
We aim to find 64 participants to volunteer to take part in this experiment. Participants will be students from the University of Aberdeen. Some will be compensated with course credit and some will be paid \pounds 15 for their time. Sample size was determined in part due to constraints with counter-balancing; there are 16 different possible orders of tasks/conditions; we will run four participants in each order for a total of 64. All participants will sign a form giving informed consent. The study has already been approved by the University of Aberdeen Psychology Ethics Committee.

@@

Stimuli consisted of arrays of black oriented line segments against a grey background. The target was oriented $45^{\circ}$ clockwise, while the distractor items had a random orientation with a mean of $45^{\circ}$ anti-clockwise. The variance was low ($18^{\circ}$) on one half of the display to create a homogeneous texture, and high ($95^{\circ}$) on the other side to create a heterogeneous texture. This means that when the target is present on the homogeneous side of the stimulus, it can be easily be detected with peripheral vision, but when it is in the heterogeneous half, it is much harder to detect. There were a total of 160 trials and homo- and heterogeneous sides of the display were randomly varied from trial to trial.

The position of the dominant eye was recorded using a desktop-mounted EyeLink 1000 eye
tracker (SR Research, Canada) sampling eye position at 1000 Hz.
This paradigm was carried out twice to give us an estimate of how consistent participants are in their search strategy over time. The two sessions were identical.

@@

In order to characterise an individual's behaviour in this task, we will compute the proportion of the first $n$ fixations that were on heterogeneous (difficult) side of the stimuli, over all target absent trials\footnote{Only take correct trials?}. \cite{nowakowsak2017} demonstrated a strong correlation between an this metric (for $n=5$) and reaction times ($r=.53$). However, a re-analysis of their data shows that an even stronger correlation is obtained with $n=3$.

@@

\subsection{Split-half Array Search}
Our results are broadly in line with \cite{nowakowsak2017}. The correlation between accuracy and reaction times between the two sessions is shown in Figure \ref{fig:splithalf_summary}(a, b). We can clearly see that there are large differences from one participant to the next in terms of both the proportion of hard targets found, and reaction times. Furthermore, test-retest reliability appears to be reasonable, with correlations of around $r = 0.78$ (the value of $r = 0.71$ or easy targets is slightly lower, likely due to the restricted range).
